|

### 2023-07-25 journal/04-results.Rmd
added number of bootstraps

```{r}
#| label: fig_rankings_boot
#| fig.cap: "Distributions of player effects for top 10 pass rushers in each position (defensive end, outside linebacker, defensive tackle, nose tackle) by median varying intercept."
#| fig.width: 6.3
#| fig.height: 6
source(here("scripts", "10_multilevel_mod.R"))
fig_rankings_boot
```

>>>>

```{r}
#| label: fig_rankings_boot
#| fig.cap: "Distributions of player effects (obtained from 1,000 bootstrap samples) for top 10 pass rushers in each position (defensive end, outside linebacker, defensive tackle, nose tackle) by median varying intercept."
#| fig.width: 6.3
#| fig.height: 6
source(here("scripts", "10_multilevel_mod.R"))
fig_rankings_boot
```

### 2023-07-25 journal/05-discussion.Rmd
added number of bootstraps

Our multilevel model, however, is subject to several limitations.
We only account for players directly involved as the pass rusher or nearest blocker, on top of team-level effects.
The nested structure of our model enforces positive dependence between pass rushers on the same team, which may not be true.
For instance, if one defender is known to be an elite pass rusher then the opposing team may focus their blocking efforts on this player. 
This could leave the path open for another player to rush the quarterback with ease, resulting in higher STRAIN values.
As shown in Figure \ref{fig:fig_rankings_boot}, the first- and fourth-ranked defensive ends Myles Garrett and Takkarist McKinley were teammates on the Cleveland Browns during the first eight weeks of the 2021 NFL season.
McKinley is a surprising name on our list and we suspect that his high rank is mostly due to playing on the same defensive unit with Garrett, who is highly-regarded as an great pass rusher.
In order to capture this type of behavior, we could consider modeling an aggregate STRAIN across pass rushers with a regularized adjusted plus-minus (RAPM) regression approach.
The use of RAPM techniques has been successfully demonstrated in American football by @sabin2021estimating, which accounts for all players on the field with Bayesian hierarchical models.
We leave this type of analysis for future work, which will require careful consideration of available informative priors [@matano2023augmenting].

>>>>

Our multilevel model, however, is subject to several limitations.
We only account for players directly involved as the pass rusher or nearest blocker, on top of team-level effects.
The nested structure of our model enforces positive dependence between pass rushers on the same team, which may not be true.
For instance, if one defender is known to be an elite pass rusher then the opposing team may focus their blocking efforts on this player. 
This could leave the path open for another player to rush the quarterback with ease, resulting in higher STRAIN values.
As shown in Figure \ref{fig:fig_rankings_boot}, the first- and fourth-ranked defensive ends Myles Garrett and Takkarist McKinley were teammates on the Cleveland Browns during the first eight weeks of the 2021 NFL season.
McKinley is a surprising name on our list and we suspect that his high rank is mostly due to playing on the same defensive unit with Garrett, who is highly-regarded as a great pass rusher.
In order to capture this type of behavior, we could consider modeling an aggregate STRAIN across pass rushers with a regularized adjusted plus-minus (RAPM) regression approach.
The use of RAPM techniques has been successfully demonstrated in American football by @sabin2021estimating, which accounts for all players on the field with Bayesian hierarchical models.
We leave this type of analysis for future work, which will require careful consideration of available informative priors [@matano2023augmenting].
